Refinements for open automata

### 2022-03-11 2021-Refinement/paper/refinementarticle.tex
proof thm3 in progress

We can deduce for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ we have:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
 \end{multline*}	
Therefore, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land\\
			 \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}
And finally By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}	
Because of the independence of the substitution domains, we get the expected formula:
	\begin{multline*}
  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{multline*}

@@

According to how the transition $t_{12}$ is built we have to consider both cases to prove the following:
 $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in {J^1_{1}}^{\prime}:\quad &  J'_{13} \cap H'  
=((J^{2 \prime}_{1} \uplus J'_{3x}) \setminus \mbrc{k}) \cap ((H\uplus J_1) \setminus\{k\} )\\
& =((J^{2 \prime}_{1} \cap (H\uplus J_1)) \uplus (J'_{3x} \cap  (H\uplus J_1)))\setminus \mbrc{k}\\
& =((J^{2 \prime}_{1} \cap  J_1)) \uplus (J'_{3x} \cap H))\setminus \mbrc{k}\text{ since }  J^{2 \prime}_{1}\cap H = \emptyset \text{ and } J'_{3x}\cap J_1 = \emptyset  \\
& =(J^{2 \prime}_{1} \uplus (J'_{3x} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}\subseteq J_1\\
& =(J^{1 \prime}_{1} \uplus (J'_{2} \cap H))\setminus \mbrc{k}  \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
&  =((J^{1 \prime}_{1} \cap J_{1}) \uplus (J'_{2} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1} \subseteq J_1 \\
& = (J'_{2} \cap (J_1 \uplus H)) \uplus (J^{1 \prime}_{1}\cap (J_1 \uplus H))\setminus \mbrc{k} \text{ since } 
J_1 \cap  J'_{2}= \emptyset \text{ and } H \cap J^{1 \prime}_{1} = \emptyset\\
& = ((J'_{2} \uplus J^{1 \prime}_{1})\setminus \mbrc{k}) \cap   ((J_1 \uplus H)\setminus \mbrc{k})\\
& = J'_{12}\cap H'\\
\text{if } k \notin {J^1_{1}}^{\prime}:\quad &	J'_{13x} \cap H'  = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
& = \mpar{J'_2\cap H } \text{ since } J'_2 \cap H = J'_{3x} \cap H\\
& = \mpar{J'_{12}\cap H' } \text{ since } J_2\cap J'_1=\emptyset \land k\not\in {J^1_{1}}^{\prime}
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in {J^1_{1}}^{\prime}$:\\
As before, the proof  is based  on the fact that the composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. As  $\alpha^1_{1}=\alpha^2_{1}$  we deduce: 
$\alpha_{12} = \alpha_{13x}$. In addition we have:\\
 $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$\\

Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]\\
Third, considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{1}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$.

@@

By entering all the intermediate results  into the formula $(*)$ we get:
\begin{multline*}
%\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \wedge  \mpar{g^1_1  \wedge \alpha_2=\beta^1_{1k}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
\implies\hspace{5em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
		\end{array}} \wedge    \mpar{g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}}
\end{multline*}	
which can be simplified as follows:
\begin{multline*}
%\everymath{\displaystyle}
V_{12} \uplus V_{13} \uplus \fvars{t_{13x}} \vdash\\ R\mpar{s_2, s_3} \wedge g_{12} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
\implies\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
			 g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
		\end{array}} 
\end{multline*}

>>>>

We can deduce for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ we have:
\begin{multline*}
V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
 \end{multline*}	
Therefore, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land\\
			 \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}
And finally by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}	
Because of the independence of the substitution domains, we get the expected formula:
	\begin{multline*}
  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{multline*}

@@

According to how the transition $t_{12}$ is built we have to consider both cases to prove the following:
 $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in {J^1_{1}}^{\prime}:\quad &  J'_{13} \cap H'  
=((J^{2 \prime}_{1} \uplus J'_{3x}) \setminus \mbrc{k}) \cap ((H\uplus J_1) \setminus\{k\} )\\
& =((J^{2 \prime}_{1} \cap (H\uplus J_1)) \uplus (J'_{3x} \cap  (H\uplus J_1)))\setminus \mbrc{k}\\
& =((J^{2 \prime}_{1} \cap  J_1)) \uplus (J'_{3x} \cap H))\setminus \mbrc{k}\text{ since }  J^{2 \prime}_{1}\cap H = \emptyset \text{ and } J'_{3x}\cap J_1 = \emptyset  \\
& =(J^{2 \prime}_{1} \uplus (J'_{3x} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}\subseteq J_1\\
& =(J^{1 \prime}_{1} \uplus (J'_{2} \cap H))\setminus \mbrc{k}  \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
&  =((J^{1 \prime}_{1} \cap J_{1}) \uplus (J'_{2} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1} \subseteq J_1 \\
& = (J'_{2} \cap (J_1 \uplus H)) \uplus (J^{1 \prime}_{1}\cap (J_1 \uplus H))\setminus \mbrc{k} \text{ since } 
J_1 \cap  J'_{2}= \emptyset \text{ and } H \cap J^{1 \prime}_{1} = \emptyset\\
& = ((J'_{2} \uplus J^{1 \prime}_{1})\setminus \mbrc{k}) \cap   ((J_1 \uplus H)\setminus \mbrc{k})\\
& = J'_{12}\cap H'\\
\text{if } k \notin {J^1_{1}}^{\prime}:\quad &	J'_{13x} \cap H'  = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
& = \mpar{J'_2\cap H } \text{ since } J'_2 \cap H = J'_{3x} \cap H\\
& = \mpar{J'_{12}\cap H' } \text{ since } J_2\cap J'_1=\emptyset \land k\not\in {J^1_{1}}^{\prime}
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in {J^1_{1}}^{\prime}$:\\
As before, the proof  is based  on the fact that the composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. As  $\alpha^1_{1}=\alpha^2_{1}$  we deduce: 
$\alpha_{12} = \alpha_{13x}$. In addition we have:\\
 $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$

Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  
\[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]
Third, considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{1}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$.

@@

By entering all the intermediate results  into the formula $(*)$ we get:
\begin{multline*}
%\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \wedge  \mpar{g^1_1  \wedge \alpha_2=\beta^1_{1k}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
\implies\hspace{5em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
		\end{array}} \wedge    \mpar{g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}}
\end{multline*}	
which can be simplified and rewritten as follows:
\begin{multline*}
%\everymath{\displaystyle}
V_{12} \uplus V_{13} \uplus \fvars{t_{13x}} \vdash\\ R\mpar{s_2, s_3} \wedge g_{12} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
\implies\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
			 g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
		\end{array}} 
\end{multline*}	
For any transition $t_1$ in $A_1$ relying $s_1$ and $s^{\prime}_1$ and for each $x \in X$ we have:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash\\
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1 
 \end{multline*}	
We can deduce for all  $x \in X$ the following statement:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash\\
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\,\,\everymath{\displaystyle}\bigwedge_\subbox{v_1\in V_1}\!\! \mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1 }
 \end{multline*}	
Therefore, we get:
\begin{multline*}
%\everymath{\displaystyle}
V_{12} \uplus V_{13} \uplus \fvars{t_{13x}} \vdash\\ R\mpar{s_2, s_3} \wedge g_{12} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1 \wedge s^1_1 = s^2_1
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
			 g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge\bigwedge_\subbox{v_1\in V_1}\!\! \mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1
		\end{array}   } 
		\end{multline*}

Considering the hypothesis that 	\(A_1\subst{A_2}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have  for all $t_{12} \in T_{12}$:
\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]

\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
